Regular singular Volterra equations on complex domains

### 2023-08-15 reg-sing-volterra.tex
Start revising proof that prototype solution works

\subsubsection{Construction}\label{sec:construction}
\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
    Let $\psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \psi_0 = -\frac{q}{p} \psi_0\;d\zeta $. Hence, for every $a\in\Omega$ 
    \begin{align*}
        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\psi_0 d\zeta \\
        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0 d\zeta\\
        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\psi_0  \\
    \end{align*}

    Now we claim $\lim_{a\to 0}\psi_0(a)=0$: in fact, choose some $\varepsilon>0$. By Condition~\eqref{cond:sing}, we can find $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
\begin{equation}\label{eqn:limit_h1}
\left|\frac{q(a')}{p(a)} - \frac{\tau}{\zeta(a)}\right|<\varepsilon
\end{equation}
 % notice that $|p(a)|\leq \varepsilon$ for $|zeta(a)|\leq \delta$, while $|q(a')-\ell|\leq \varepsilon$ for $|\zeta(a')|\leq \delta$ and $\ell>0$. 
 Then, we choose $b\in\Omega$ such that $\tfrac{\delta}{2}=|\zeta(b)|$.
\begin{align*}
-\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
\end{align*}
Exponentiating both sides, we see that
\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
The exponential factor is bounded between $\exp\big({-\tfrac{3}{2}\varepsilon\delta}\big)$ and $\exp\big(\tfrac{3}{2}\varepsilon\delta\big)$ for all points $a$ in our chosen neighborhood of $\zeta = 0$. We deduce that $\hardpart  f_0=f_0$. 
\end{proof}

>>>>

\subsubsection{Construction}\label{sec:construction}
\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
Let
\[ \psi_0(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right), \]
so $\solproto = \frac{p(b)}{p} \psi_0$. Observing that $d\psi_0 = -\frac{q}{p} \psi_0\;d\zeta$, we can write $\hardpart \solproto$ in terms of an integral of $d\psi_0$. For each $a \in \Omega$, we have
\begin{align*}
\big[\hardpart \solproto\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\solproto\;d\zeta \\
&= -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{p(b)}{p}\psi_0\;d\zeta \\
&= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0\;d\zeta\\
&= \frac{p(b)}{p(a)} \int_{\zeta=0}^{a}\;d\psi_0.
\end{align*}

To evaluate this improper integral using the fundamental theorem of calculus, we need to find $\lim_{a \to 0} \psi_0(a)$. This limit turns out to be $0$, as shown by the following argument. Choose some $\varepsilon>0$. By Condition~\eqref{cond:sing}, we can find a radius $\delta>0$ such that
\begin{equation}\label{eqn:limit_h1}
\left|\frac{q(a')}{p(a)} - \frac{\tau}{\zeta(a)}\right|<\varepsilon
\end{equation}
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$. \textcolor{orange}{[...]}
\begin{align*}
-\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
\end{align*}
Exponentiating both sides, we see that
\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
The exponential factor is bounded between $\exp\big({-\tfrac{3}{2}\varepsilon\delta}\big)$ and $\exp\big(\tfrac{3}{2}\varepsilon\delta\big)$ for all points $a$ in our chosen neighborhood of $\zeta = 0$. We deduce that $\hardpart  f_0=f_0$. 
\end{proof}
